Summary of the Iberian Bees Database

### 2022-02-27 Manuscript/Summary/Summary.Rmd
Telling git to don't ignore capital letters

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code courtesy of Paco Rodriguez.
library(sf)
library(raster)
library(rasterVis)

crs.geo <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
crs.laea <- "+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs"

dat <- subset(data, !is.na(Latitude) & !is.na(Longitude))
datos.sf <- st_as_sf(dat,
                     coords = c("Longitude", "Latitude"),
                     crs = crs.geo)

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code courtesy of Paco Rodriguez.
library(sf)
library(raster)
library(rasterVis)
library(tidyverse)
crs.geo <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
crs.laea <- "+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs"

library(data.table)
data <- read.table("../../Data/iberian_bees.csv.gz",  header=T, quote="\"", sep=",")

#Prepare data
data$Longitude <- as.numeric(data$Longitude)
data$Latitude <- as.numeric(data$Latitude)
data <- data %>% filter(!is.na(Latitude) & !is.na(Longitude))
#Keep points on balearic islands
data_1 <- data %>% filter(Province=="Balears, Illes")
data_1$Country_1 <- NA

#Filter points in Spain and Portugal
data$Country_1 <- NA
data$Country_1 <- maps::map.where(x = data$Longitude, y = data$Latitude)
data <- data %>% filter(Country_1=="Spain" | Country_1=="Portugal")
#Rbind points that are in Spain with the ones of Balearic islands
dat <- rbind(data, data_1)

datos.sf <- st_as_sf(dat,
                     coords = c("Longitude", "Latitude"),
                     crs = crs.geo)
